---
title: "Class_4"
output: html_document
date: "2025-09-18"
---

```{r}
library(tidyverse)
```

Let's import the datasets

```{r}
litters_df=
  read_csv("data/FAS_litters.csv", na = c("NA",".",""))
litters_df =
  janitor::clean_names(litters_df)

pups_df=
  read_csv("data/FAS_pups.csv", skip = 3, na = c("NA",".",""))
pups_df =
  janitor::clean_names(pups_df)

```

## 'select'

`select` selects variables from my dataframe.

this will give new data set with just these 3 variables
select specific variables
```{r}
select(litters_df, group, litter_number, gd0_weight)
```
select a range
```{r}
select(litters_df, group:gd_of_birth)
```
select by removal
```{r}
select(litters_df, -group)
select(litters_df, -group:gd_of_birth)
```
select by prefix
```{r}
select(litters_df, group, starts_with("gd"))
```
rearrange by selecting
```{r}
select(litters_df, starts_with("gd"), group)
select(litters_df, litter_number, everything())

relocate(litters_df, litter_number)
```
rename by selecting
here we rename group and keep everything
```{r}
select(litters_df, GROUP = group, everything())
rename(litters_df, GROUP = group)
```

what if i only select one variable...?
```{r}
select(litters_df, group)

pull(litters_df, group)
```
but almost never use pull always use select.
